Teaching Dossier

### 2019-11-15 CUT/teaching-philosophy.tex
Working up to Outside the Classroom section

\subsection{Teaching Assistantships}
\paragraph{}Over the course of my graduate studies at the University of Waterloo I have had the priviledge of being a teaching assistant for many different courses. The standard duties of a TA in our department, Combinatorics and Optimization, involve grading, proctoring exams, and holding office hours to support students seeking help. Below I have described the courses to which I was assigned a teaching assistantship, as well as any additional duties I was responsible for in each course.
\bigskip

@@

\paragraph{}During my undergraduate degree at the University of Windsor I had the opportunity to be a teaching assistant during my final year of study. I was assigned to TA the introductory linear algebra course for first years in the Fall term of $2014$, and the introductory course on mathematical proof in the Winter term of $2015$.

\section{Teaching Strategies}

>>>>

\subsection{Teaching Assistantships}
\paragraph{Graduate TA}Over the course of my graduate studies at the University of Waterloo I have had the priviledge of being a teaching assistant for many different courses. The standard duties of a TA in our department, Combinatorics and Optimization, involve grading, proctoring exams, and holding office hours to support students seeking help. Below I have described the courses to which I was assigned a teaching assistantship, as well as any additional duties I was responsible for in each course.
\bigskip

@@

\paragraph{Undergraduate TA}During my undergraduate degree at the University of Windsor I had the opportunity to be a teaching assistant during my final year of study. I was assigned to TA the introductory linear algebra course for first years in the Fall term of $2014$, and the introductory course on mathematical proof in the Winter term of $2015$. Both courses saw me giving a weekly tutorial based on the assigned problem set for that week. I was also responsible during this time for working in the University's tutoring centre. My role there was to provide one-on-one or small group support to any students who came in with questions about math courses at the university. This opportunity was an interesting challenge because it required a broad understanding of the courses offered by the university that particular term, since any student studying math could approach me expecting to receive help with their coursework.

\subsection{Guest Lectures}
\paragraph{Introduction to Game Theory}
As I discussed in Section $2.2$ I have had the opportunity to give guest lectures in CO $456$, Waterloo's mathematically rigorous introduction to game theory. In the Fall $2018$ offering, I gave a single $80$ minute lecture on the topic of correlated equilibria. This was the first time that particular topic was taught in the course. As such, I was responsible for designing not only the lesson plan from scratch, but also preparing suitable exam and assignment problems related to the material. I used a post-test technique in the lecture where I saved the last ten minutes of instruction time for the students to solve a hands-on problem in class of computing a correlated equilibrium for a small strategic game. The head instructor of the course, who was observing my lecture, commented that he found the technique to be a very engaging way for the students to review the material and he would be interested in trying it himself in the future.

I also had an opportunity to give a series of three $50$ minute guest lectures during the Fall $2019$ offering of CO $456$ during a week where the head instructor was travelling for a conference. They had just finished up a section of course material, and I was given free reign to choose the next topic. I chose Nash's Theorem that every finite strategic game has a mixed Nash equilibrium. The first two lectures concentrated on the fundamental tools needed to prove the theorem: Sperner's Lemma and Brouwer's Fixed Point Theorem. The last lecture discussed the combination of these two results to obtain Nash's Theorem. I used a strategy of providing a high-level outline at the start and end of each lecture so that students could maintain a big picture view of the proof of Nash's Theorem as we progressed through the technical details throughout the week.

\paragraph{Microteaching} During my Master's degree I took a professional teaching development program through the University of Waterloo's Centre for Teaching Excellence called the Fundamentals of University Teaching program. As part of this program, participants were required to give a series of three $15$ minute mini-lectures to their peers and the facilitators of the program. The lectures were supposed to highlight three different areas: a subject suitable for first year students of your discipline, a subject related to your area of research, and a specific teaching method. I chose the Gaussian elimination process for solving linear systems from a first year linear algebra course, the prisoner's dilemma from game theory, and the Think-Pair-Share technique respectively for my three lectures. These sessions were a valuable learning experience. The feedback from peers and teaching experts was invaluable, and the tight time constraints really helped me hone my lesson planning and time management skills in the classroom. 
\subsection{Outside the Classroom}
\paragraph{TORCH}Teaching is a major part of my life, and I believe an important part of teaching is inspiring young students to pursue higher education. The Operations Research Challenge, TORCH for short, is a contest given to high school students which focuses on solving algorithmic operations research problems. The contest is hosted simultaneously at the Universities of Waterloo, Toronto, and Concordia. As an outreach program, it aims to promote awareness and interest in operations research among high school students. I have been a volunteer for the annual contest in $2018$ and $2019$. In this role I was responsible for giving contest students real time feedback on their proposed solutions, as well as discussing in between sessions what studying operations research in university is like and encouraging students to pursue studies in STEM.

In $2020$ I am transitioning into an executive role on Waterloo's organizing team. My role will be to lead to the creative design of problem sets for the contest. I will be responsible for creating contest problems which are challenging, engaging, relevant to student interests, and accessible to students of all background levels. In addition to creating problems myself, I will be overseeing other question writers to ensure a high standard of quality in questions provided for the contest.

\paragraph{Brazilian Jiu-Jitsu}
\section{Teaching Strategies}
